---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# regcensusAPI

<!-- badges: start -->
<!-- badges: end -->

The goal of regcensusAPI is to provide an easy way for researchers to access regulatory restrictions data from  the Mercatus Center at George Mason University, RegData. RegData quantifies the volume of regulatory restrictions in various jurisdictions, from national to subnational. For more information about RegData, visit [QuantGov](https://www.quantgov.org) website.

## Installation

You can install the released version of regcensusAPI from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("regcensusAPI")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("QuantGov/regcensus-api-client-R")
```
## Usage

Using the API is easy. First, you would want to find out what topics are covered.

```{r example}
library(regcensusAPI)
## basic example code
get_topics()
```

All data are further grouped into *series*. The function **get_series_period()** returns the list of data series, the jurisdictions, and the periods for which data are available.
```{r}
get_series_period()
```

For more information on how to fully utilize regcensusAPI to obtain regulatory restrictions data, check out the vignette accompanying the package.



